---
title: "Titles are boring"
author: Ian McCarthy
date: January 2021
geometry: "left=2cm,right=2cm,top=1cm,bottom=2cm"
fontsize: 11pt
subparagraph: yes
header-includes:
   - \usepackage{setspace}
   - \singlespacing
   - \usepackage{titlesec}
   - \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
output: 
  pdf_document2:
    keep_tex: TRUE
    toc: FALSE
    number_sections: FALSE
bibliography: 'BibTeX_Library.bib'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, modelsummary, scales, knitr, kableExtra)
```

```{r, include=FALSE}
load("data/R_workspace.Rdata")
```

### Abstract:
Does spending improve health? @martin2008 says yes. We find some cool stuff that says something no one has ever thought of before. We find average spending of `r dollar(mean.exp)`. What we find is totally accurate and indisputable, yet completely novel and significant. This is the best paper ever. I have no reservations in claiming that I will win a Nobel Prize because of this paper. Having written this paper, I can die a happy man.

# References
