---
title: "Titles are great"
author: Ian McCarthy
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
fontsize: 12pt
subparagraph: yes
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{titlesec}
   - \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
   - \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
output: 
  pdf_document2:
    keep_tex: TRUE
    toc: FALSE
bibliography: 'BibTeX_Library.bib'
---

```{r setup, include=FALSE}
options(dplyr.summarise.inform = FALSE)
knitr::opts_chunk$set(echo = TRUE)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, modelsummary, knitr, kableExtra)
```

```{r, include=FALSE}
load("data/R_workspace.Rdata")
```

\setstretch{1.5}

# Introduction
Does spending improve health? @martin2008 says yes. We find some cool stuff that says something no one has ever thought of before. We find average spending of `r dollar(mean.exp)`. What we find is totally accurate and indisputable, yet completely novel and significant. This is the best paper ever. I have no reservations in claiming that I will win a Nobel Prize because of this paper. Having written this paper, I can die a happy man.


# Model
For our discrete choice model, we assume that household $i$ chooses the plan $j$ that maximizes their utility,
\begin{equation}
u_{ij} = \alpha_{i}p_{ij} + \beta x_{j} + \gamma d_{i} + \xi_{j} + \varepsilon_{ij}, (\#eq:utility)
\end{equation}
where $p_{ij}$ denotes the premium for plan $j$, $x_{j}$ denotes a vector of product characteristics, $d_{i}$ denotes a vector of household characteristics, $\xi_{j}$ captures unobserved product characteristics, and $\varepsilon_{ij}$ is an error term assumed to follow a type I extreme value distribution. We allow for heterogeneities in price elasticities across households by parameterizing $\alpha_{i}$ in Equation \@ref(eq:utility), $$\alpha_{i} = \alpha + \theta d_{i}.$$ In our estimation, this amounts to including a full set of interactions between $d_{i}$ and $p_{ij}$.


# Results
We plot spending and mortality in Figure \@ref(fig:plot1).

```{r plot1, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Spending and Mortality"}
plot1
```


We also estimate by OLS the relationship between spending and mortality. Results are summarized in Table \@ref(tab:ols).

```{r ols, echo=FALSE, results='asis', message=F}
modelsummary(list(reg1,reg2,reg3),
             coef_omit="Intercept",
             statistic="conf.int",
             conf_level=0.95,
             title="Regression Results",
             coef_rename = c("exp_1000" = "Expenditures per Capita ($1000s)"),
             gof_omit = 'R2|AIC|BIC|Log')
```


\clearpage
\newpage

# References